Temporal ordering and registration of imaging data in cross--sectional studies of development

### 2014-03-27 image_analysis_paper/pnas_draft.tex
updated paper figures; added toy example

\begin{figure}
\begin{subfigure}{0.25\textwidth}
\includegraphics[width=\textwidth]{fig2a}
\caption{}
\label{subfig:images_scrambled}
\end{subfigure}
\begin{subfigure}{0.25\textwidth}
\includegraphics[width=\textwidth]{fig2b}
\caption{}
\label{subfig:images_hand_ordered}
\end{subfigure}
\caption{{\em Drosophila} data. (a) Dorsal-ventral images of {\em Drosphila} embryos, each fluorescentally stained for Dorsal (green) and dpERK (red). (b) Images from (a), now registered using the location of the Dorsal peak, and temporally ordered using cellularization.} 
\label{fig:fluorescent_images}
\end{figure}

@@

\begin{figure*}
\begin{subfigure}{0.17\textwidth}
\includegraphics[width=\textwidth]{illustrate_1d}
\caption{}
\label{subfig:1d_image_example}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{unregistered_unordered_1d}
\caption{}
\label{subfig:1d_unaligned_unordered}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{registered_unordered_1d}
\caption{}
\label{subfig:1d_aligned_unordered}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{registered_ordered_1d}
\caption{}
\label{subfig:1d_aligned_ordered}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{registered_ordered_vdm_1d}
\caption{}
\label{subfig:1d_aligned_ordered_vdm}
\end{subfigure}
\caption{Illustration of methodologies using one-dimensional profiles. (a) One-dimensional concentration profile on a ring (top), and the corresponding profile on a line (bottom). Rotation of the ring corresponds to shifting the line left and right (with periodic boundary conditions). (b) The concentration profiles corresponding to the images in Figure \ref{fig:fluorescent_images}. Each row in the array corresponds to one image. (c) The concentration profiles in (b), now registered using angular synchronization. (d) The concentration profiles in (c), now temporally ordered using diffusion maps. The profiles are sorted according to the value of the first non-trivial DMAPS component, $\phi_2$. (e) The concentration profiles in (b), now simultaneously registered and temporally ordered using vector diffusion maps. The profiles are sorted according to the value of the first non-trivial VDM component, $\psi_{1, 3}$.}
\label{fig:1d_demo}
\end{figure*}

\begin{figure*}
\begin{minipage}{0.6\textwidth}
\begin{subfigure}{\textwidth}
%\includegraphics[width=\textwidth]{registered_ordered_vdm_2d}
\includegraphics[width=\textwidth]{test}
\caption{}
\label{subfig:images_vdm}
\end{subfigure}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{rank_corr_vdm}
\caption{}
\label{subfig:rank_corr}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{bootstrap_rank_corr_color}
\caption{}
\label{subfig:bootstrap}
\end{subfigure}
\end{minipage}
\caption{(a) The images in Figure~\ref{fig:fluorescent_images}, aligned and temporally ordered using vector diffusion maps. The images are sorted according to the value of the first non-trivial VDM component, $\psi_{1, 4}$. (b) The rank correlation between the ordering of the images in (a) using vector diffusion maps, and the ordering of in the images in Figure~\ref{subfig:images_hand_ordered}, obtained using cellularization. (c) The rank correlation coefficient between the VDM ordering and the cellularization ordering as a function of the number of data points. }
\end{figure*}

>>>>

\begin{figure}
\includegraphics[width=0.5\textwidth]{unregistered_unordered_2d}
\caption{}
\label{fig:fluorescent_images}
\end{figure}

@@

\begin{figure*}
\begin{subfigure}{0.17\textwidth}
\includegraphics[width=\textwidth]{illustrate_toy}
\caption{}
\label{subfig:1d_image_example}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{unregistered_unordered_toy}
\caption{}
\label{subfig:1d_unaligned_unordered}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{registered_unordered_toy}
\caption{}
\label{subfig:1d_aligned_unordered}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{registered_ordered_toy}
\caption{}
\label{subfig:1d_aligned_ordered}
\end{subfigure}
\begin{subfigure}{0.2\textwidth}
\includegraphics[width=\textwidth]{registered_ordered_vdm_toy}
\caption{}
\label{subfig:1d_aligned_ordered_vdm}
\end{subfigure}
\caption{Illustration of methodologies using one-dimensional profiles. (a) One-dimensional concentration profile on a ring (top), and the corresponding profile on a line (bottom). Rotation of the ring corresponds to shifting the line left and right (with periodic boundary conditions). (b) The concentration profiles corresponding to the images in Figure \ref{fig:fluorescent_images}. Each row in the array corresponds to one image. (c) The concentration profiles in (b), now registered using angular synchronization. (d) The concentration profiles in (c), now temporally ordered using diffusion maps. The profiles are sorted according to the value of the first non-trivial DMAPS component, $\phi_2$. (e) The concentration profiles in (b), now simultaneously registered and temporally ordered using vector diffusion maps. The profiles are sorted according to the value of the first non-trivial VDM component, $\psi_{1, 3}$.}
\label{fig:1d_demo}
\end{figure*}

\begin{figure*}
\begin{minipage}{0.6\textwidth}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{registered_ordered_vdm_2d}
\caption{}
\label{subfig:images_vdm}
\end{subfigure}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{registered_ordered_vdm_1d}
\caption{}
\label{subfig:rank_corr}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{registered_ordered_hand}
\caption{}
%\label{subfig:bootstrap}
\end{subfigure}
\end{minipage}
%\caption{(a) The images in Figure~\ref{fig:fluorescent_images}, aligned and temporally ordered using vector diffusion maps. The images are sorted according to the value of the first non-trivial VDM component, $\psi_{1, 4}$. (b) The rank correlation between the ordering of the images in (a) using vector diffusion maps, and the ordering of in the images in Figure~\ref{subfig:images_hand_ordered}, obtained using cellularization. (c) The rank correlation coefficient between the VDM ordering and the cellularization ordering as a function of the number of data points. }
\end{figure*}
